DraftOne

### 2016-07-22 writing/JSSDraft/JSSDraft.Rmd
Adding Gryparis

>>>>

\citet{Gryparis2009} compared approaches to fitting health models using predicted exposures featuring spatial misalignment.  The authors considered four levels of heterogeneity in exposure values over a geographic area and simulated exposure data for each.  They simulated both continuous and binary health outcomes, which could be done using eesim, and evaluated several approaches to relating exposure to outcome, including Bayesian and RC-OOS approaches.  Their simulation results suggested that several approaches may be appropriate to discover relationships in spatially misaligned data.
